Chaotic dispersal of tidal debris

### 2015-09-21 ms.tex
added density plot

% Figure ??
\begin{figure}[!p]
\begin{center}
\includegraphics[width=\textwidth]{figures/potential.pdf}
\caption{Equipotential contours for the triaxial NFW potential considered in this work. There are eight contour levels evenly spaced and linear in the value of the potential. } \label{fig:potential}
\end{center}
\end{figure}

>>>>

% Figure ??
%\begin{figure}[!p]
%\begin{center}
%\includegraphics[width=\textwidth]{figures/potential.pdf}
%\caption{Equipotential contours for the triaxial NFW potential considered in this work. There are eight contour levels evenly spaced and linear in the value of the potential. } \label{fig:potential}
%\end{center}
%\end{figure}
\begin{figure}[p]
\centering
    \subfloat{
      \includegraphics[width=0.45\textwidth]{figures/potential.pdf}
    }
    \subfloat{
      \includegraphics[width=0.45\textwidth]{figures/density-contours.pdf}
    }
\caption{\chchchanges{Equipotential contours (left) and isodensity contours (right) for the triaxial NFW potential considered in this work. For the potential plot there are eight contour levels evenly spaced and linear in the value of the potential. For the density plot there are eight contour levels logarithmically spaced from $10^4~\msun~{\rm kpc}^{-3}$ to $10^7~\msun~{\rm kpc}^{-3}$.}}
\label{fig:potential}
\end{figure}
